%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA [0pt].0 (http://creativecommons.org/licenses/by-nc-sa/[1pt].0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,letterpaper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[scale=0.8, top=0.4in, bottom=0.4in]{geometry} % Reduce document margins
\usepackage{tgpagella}
\usepackage{microtype}
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Ashley E.} % Your first name
\familyname{Hedberg} % Your last name

% All information in this block is optional, comment out any lines you don't need
\mobile{(804) 357-4820}
\email{ashley.hedberg@tufts.edu}
\address{61 Frederick Avenue}{Medford, MA 02155}

%----------------------------------------------------------------------------------------

\begin{document}

\makecvtitle % Print the CV title
\vspace*{-10pt}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry[0pt]{Sept. 2011--May 2015}{Bachelor of Science}{Tufts University School of
Engineering}{Medford, MA}{\textit{GPA: 3.96}}{Major: Computer Science \\ Second Major: Applied Mathematics}  % Arguments not required can be left empty

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\vspace*{-5pt}

\section{Work Experience}

\cventry[0pt]{May 2014--Aug. 2014}{Software Engineering Intern}{Google}{Cambridge, MA}{}{
\begin{itemize}
\item Improved the testing framework of Google's content delivery network
\item Analyzed results of content delivery network load tests using statistical methods
\item Created an internal service for team members to search for and compare load test results
\end{itemize}}

\cventry[0pt]{July 2013--Aug. 2013}{Engineering Intern}{Rapid7}{Cambridge, MA}{}{
\begin{itemize}
\item Deployed end-user agent to collect information about activity on a Windows machine
\item Built web service to convert agent data into monitoring statistics
\item Developed user interface for a company-facing cloud monitoring service
\end{itemize}}

\cventry[0pt]{Sept. 2013--Present}{Engineering Outreach Intern}{Tufts University Office of Undergraduate Admissions}{Medford, MA}{}{
\begin{itemize}
\item Recruit and organize volunteers for Engineering Open House events
\item Contribute to and improve engineering-related content on admissions website
\item Redesigned engineering tour route and developed training program for engineering tour guides
\end{itemize}}

\cventry[0pt]{Jan. 2013--Present}{Teaching Fellow, Data Structures; Teaching
Assistant, Networks}{Tufts University Department of Computer Science}{Medford, MA}{}{
\begin{itemize}
\item Manage communications for team of undergraduate teaching assistants
\item Coordinate with class professor to plan and lead weekly implementation laboratories
\item Hold weekly office hours to assist students with assignments and class material
\item Grade student projects
\end{itemize}}

%----------------------------------------------------------------------------------------
%	PROGRAMMING SKILLS
%----------------------------------------------------------------------------------------

\vspace*{-10pt}

\section{Skills}

\small
\cvitemwithcomment[0.5pt]{Languages:}{C, C++, Python, Java, JavaScript, Standard
ML, CSS, HTML}{}
\cvitemwithcomment[0.5pt]{Coursework:}{Networks, Computer Systems Security,
Concurrent Programming, Operating Systems}{}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{Awards}

\cvitemwithcomment[0.5pt]{Dean's List}{}{All Semesters}
\cvitemwithcomment[0.5pt]{Fox-Ould Scholarship Recipient}{}{June 2014}
\cvitemwithcomment[0.5pt]{Raytheon-FIRST Robotics Scholarship Recipient}{}{July 2011}
\cvitemwithcomment[0.5pt]{National Merit Scholarship Recipient}{}{Mar. 2011}

%----------------------------------------------------------------------------------------
%	LEADERSHIP
%----------------------------------------------------------------------------------------

\section{Extracurricular Activities}

\cvitemwithcomment[0.5pt]{Tufts Tap Ensemble:}{Director, Public Relations, Webmaster,
Choreographer}{Sept. 2011--Present}
\cvitemwithcomment[0.5pt]{Tufts Undergraduate Science Magazine:}{Webmaster, Copy
Editor}{Sept. 2011--Present}
\cvitemwithcomment[0.5pt]{Tufts Dance Collective:}{Choreographer}{Sept. 2011--Present}
\cvitemwithcomment[0.5pt]{Harvard-Epworth United Methodist Church Bell
Choir}{}{Sept. 2012--Present}
\cvitemwithcomment[0.5pt]{The Scientista Foundation:}{Co-Director, Public
Relations}{Sept. 2012--Present}
\cvitemwithcomment[0.5pt]{Society of Women Engineers:}{Webmaster}{Sept. 2012--Present}
\cvitemwithcomment[0.5pt]{Tufts Engineering Mentors}{}{Apr. 2013--Present}
\cvitemwithcomment[0.5pt]{Tau Beta Pi}{}{Nov. 2013--Present}
\cvitemwithcomment[0.5pt]{Tufts Undergraduate Admissions Tour Guide}{}{Jan. 2012--Apr.
2014}



\end{document}
